\Large Analyzing the Supreme Court Citation Network

### 2017-12-29 Tex/paper.tex
revising notation

Let $c_ij \in \{0,1\}$ be a binary indicator of whether case $i$ cites $j$. Furthermore, let
$$\mathcal{C}_t(N)=\{c(t)\in \{0,1\}^N: c_i(t)\in \{0,1\} \}$$ 
be the set of all possible citation combinations at time $t$. Note that the cardinality of $\mathcal{C}_t(N)$ increases exponentially for every newly added case, which results in $2^N$ elements.\\
The probability function of the ERCM is defined as
\begin{equation}
P_{\theta}(c(t)~|~c(t-))=\cfrac{\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}{\sum_{c(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}
\label{ercm}
\end{equation}
where $c(t-)\in \{0,1\}^{N \times (t-1)}$ is a matrix that indicates which cases have been citing in each other before time $t$, $\theta \in \mathbb{R}^q$ is a q-dimensional vector of parameters,  $h: \mathcal{C}_t(N) \to \mathbb{R}^q ~, ~ \c(t) \to (h_1(c(t)), \dots , h_q(c(t)))^T$ is a q-dimensional vector of different statistics and $\kappa(\theta) := \sum_{c(t)^*\in \mathcal{C}}\exp(\theta^T\cdot h(c(t)|c(t-)))$ is a normalization constant that ensures that (\ref{ercm}) defines a probability function on $\mathcal{C}_t$.\\[0.3cm]

>>>>

Let $c_{ij} \in \{0,1\}$ be a binary indicator of whether case $i$ cites $j$. Furthermore, let
$$\mathcal{C}_t=\{c(t)\in \{0,1\}^{N_t}: c_{ij}(t)\in \{0,1\} \}$$ 
be the set of all possible citation combinations for opinions issued in term $t$, where $c_{ij}(t)$ is a binary indicator of whether case $i$ cites case $j$, and case $i$ is decided at time $t$. Note that the cardinality of $\mathcal{C}_t$ increases exponentially for every newly added case.\\ The probability function of the c-TERGM  is defined as
\begin{equation}
P_{\theta}(c(t)~|~c(t-))=\cfrac{\exp\big(\theta^T\cdot h\big(c(t)~|~c(t-)\big)\big)}{\sum_{z(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(z(t)~|~c(t-)\big)\big)}
\label{ercm}
\end{equation}
where $c(t-)$ is a matrix that indicates the citations among cases decided before time $t$, $\theta \in \mathbb{R}^q$ is a $q$-dimensional vector of parameters,  $h: \mathcal{C}_t \to \mathbb{R}^q ~, ~ \c(t) \to (h_1(c(t)), \dots , h_q(c(t)))^T$ is a q-dimensional vector of different statistics and $\kappa(\theta) := \sum_{z(t)^*\in \mathcal{C}}\exp\big(\theta^T\cdot h\big(z(t)~|~c(t-)\big))$ is a normalization constant that ensures that (\ref{ercm}) defines a probability function on $\mathcal{C}_t$.\\[0.3cm]
